\subsection{Purpose}
The purpose of this document is to elaborate implementation of main technologies used in this product. We will introduce each technology from several design viewpoints such as interaction and structure. The intended audiences of this document include the client, development group, and assessors of this product. The client can understand all details of compositions that the developer will implement in this product according to this document. On the other hand, the development group can implement special plans such testing plan based on attributes of these technologies. Assessors can evaluate technologies used in the final product and then compare them with this document to ensure final product matches these technologies.  

\subsection{Scope}
In this document, technologies are separated into eight distinct pieces and each member will discuss their own pieces individually. Isaac Chan is in charge of these pieces: methods to measure performance metrics of database functionality, methods of database security, and methods of user interaction with the system. Zhi Jiang is in charge of these three pieces: S3, Amazon Kinesis, and Data Pipeline. Zhaoheng Wang is in charge of DynamoDB table design, DynamoDB Functionality implementation, and Quicksight Visualization.

\subsection{Summary}
In the document, section one will give a brief introduction for the whole document. Section two and three declare reference terms for the document. From section four, we start introducing our own technologies based on different viewpoints context, information or algorithm. For each viewpoint,we will declare the design concerns for it. This document will be in much more detail than the technology review document.  
 
