\section{References}
\begin{thebibliography}{10}
   	\bibitem{g1}"Elastic Compute Cloud (EC2) Cloud Server and Hosting – AWS", \textit{Amazon Web Services, Inc.}, 2016. [Online]. Available: https://aws.amazon.com/ec2/?nc1=h\_ls. [Accessed: 30- Nov- 2016].
    \bibitem{z1}\textit{Amazon Simple Storage Service - Developer guide}, 1st ed. Amazon Web Services, Inc, 2016, p. 3.
  	\bibitem{z2}\textit{Amazon Simple Storage Service - Developer guide}, 1st ed. Amazon Web Services, Inc, 2016, p. 196.
    \bibitem{z3}\textit{Amazon Kinesis Firehose - Developer guide}, 1st ed. Amazon Web Services, Inc, 2016, p. 2.
  	\bibitem{z4} Boto3.readthedocs.io. (2014). \textit{Boto 3 Documentation — Boto 3 Docs 1.4.4 documentation}. [online] Available at: http://boto3.readthedocs.io/en/latest/index.html [Accessed 16 Feb. 2017].
  	\bibitem{z6}\textit{AWS Data Pipeline - Developer Guide}, 1st ed. Amazon Web Services, Inc, 2016, p. 148.
  	\bibitem{z7}\textit{AWS Data Pipeline - Developer Guide}, 1st ed. Amazon Web Services, Inc, 2016, p. 136.
  
  	\bibitem{w1}"Amazon DynamoDB Developer Guide", \textit{Amazon Web Services, Inc.}, 2016. [Online]. Available: 	      http://docs.aws.amazon.com/amazondynamodb/latest/developerguide/JavaDocumentAPIWorkingWithTables.html. [Accessed: 1- DEC- 2016].
  	\bibitem{w2}"Amazon DynamoDB Developer API for Querying Tables and Indexes", \textit{Amazon Web Services, Inc.}, 2016. [Online]. Available:
  http://docs.aws.amazon.com/amazondynamodb/latest/developerguide/QueryingJavaDocumentAPI.html. [Accessed: 1- DEC- 2016].
  	\bibitem{w3}"Amazon DynamoDB Developer API for Scanning Tables and Indexes", \textit{Amazon Web Services, Inc.}, 2016. [Online]. Available:
  http://docs.aws.amazon.com/amazondynamodb/latest/developerguide/ScanJavaDocumentAPI.html. [Accessed: 1- DEC- 2016].
  	\bibitem{w4}"Amazon QuickSight User Guide", \textit{Amazon Web Services, Inc.}, 2016. [Online]. Available:
  http://docs.aws.amazon.com/quicksight/latest/user/getting-started-create-analysis-database.html. [Accessed: 1- DEC- 2016].
  
	\bibitem{i1}"Amazon Cloudwatch PutMetricData API", \textit{Amazon Web Services, Inc.}, 2016. [Online]. Available:
    
http://docs.aws.amazon.com/AmazonCloudWatch/latest/APIReference/API\_PutMetricData.html. [Accessed: 1- DEC- 2016]

	\bibitem{i2}"How to collect RDS MySQL metrics", \textit{John Matson}, 2016. [Online]. Available:
    
https://www.datadoghq.com/blog/how-to-collect-rds-mysql-metrics/. [Accessed: 1- DEC- 2016]
    
    \bibitem{i3}"Identity and Access Management (IAM)", \textit{Amazon Web Services, Inc}, 2016. [Online]. Available:
    
https://aws.amazon.com/iam/. [Accessed: 1- DEC- 2016]
  
 	\bibitem{i4}"Amazon EMR", \textit{Amazon Web Services, Inc}, 2016. [Online]. Available:
    
https://aws.amazon.com/emr/?nc2=h\_l3\_al. [Accessed: 1- DEC- 2016]

	\bibitem{i5}"Simple Linear Regression with Pure Python", \textit{ActiveState Code}, 2014. [Online]. Available:
    
http://code.activestate.com/recipes/578914-simple-linear-regression-with-pure-python/. [Accessed: 1- DEC- 2016]

\end{thebibliography}