\section{Introduction}
	\subsection{Purpose}
    OSU campuses generate data constantly from multiples sources, including computer labs, wireless usage, student devices, and many others. This quantity of data, also known as big data, can effectively represent student behaviors for information technology. For example, analysis can be run to determine common student behaviors in order to allocate OSU resources to more often used utilities. Currently, the data is very difficult to manage because it is collected from multiple sources and is impossible to analyze. The data is neither stored in the same formats nor in the same locations, meaning it is inaccessible and useful information is unable to be extracted. The purpose of this project is to unify the data onto the consistent cloud platform of Amazon Web Services, which additionally provides utilities to manage and analyze.
    \subsection{Where we currently are and what is ahead}
    In order to complete the project in a timely manner, we utilize a timeline to schedule when different tasks of the project should be finished. For week 1 and 2 of winter term, we began with data storage implementation and database table creation. Then EC2 cluster configuration starting in week 3, Python script implementation in week 5 and both completed at the end of week 6. Following week 6 we have data visualization, testing, performance and security optimizations, and finally a cost comparison to a locally hosted solution. Currently we are ahead of schedule.