\section{What remains to be done - Isaac Chan}
Due to our project task division, my tasks all fall at the end of winter term. I have kept up with the project as a whole, as well as the details of specific implementations that my teammates have completed. There are still several important parts of this project that remain to be completed.
	\subsection{Tests for Functionality}
Tests for functionality ensures that users are able to interact with the system. They will need to use different utilities for different interactions, such as monitoring resources, monitoring performance, managing data, and performing different methods of analysis. As shown previously, AWS Quicksight is able to build visualizations from the data. However, it’s unable to perform more complex analysis, such as machine learning. We plan to test basic data analysis code from AWS EMR, or Elastic MapReduce, to ensure data analysis is possible. For example, we can run a linear regression script to determine the relationship between time a user stays on a specific wireless network compared with their location on campus.\\ 

\noindent In the end, a data analyzer would use their choice of tool on the implemented database. AWS EMR will simply provide us a proof of concept that analysis is viable. When implementing these tests for functionality, I will work with a data analyzer to ensure that our database structure allows deeper analysis.
	\subsection{Measuring Performance Metrics}
Performance metrics for database functionality are important to ensure the usability of our implemented solution. We will assess performance from typical database operations: data inserts, updates, and reads. From this we can obtain a baseline for the database performance, and examine how varying data and query loads compare to the baseline. We will use AWS Cloudwatch to implement custom metrics in order to measure the performance.\\ 

\noindent Due to the subjective nature of whether or not the performance of the solution is acceptable, we will meet with current data analyzers and our client to determine if it meets expectations. We plan to provide a model for realistic usage. To create this model, we will need differing sizes of sample data to load into the database and query to obtain an accurate trend for performance, as the database size increases.
	\subsection{Database Security}
For database security, unfortunately NoSQL databases do not support external encryption tools. Therefore we must use a combination of methods to ensure security of our solution, by restricting access and preventing malicious utilization of the data. The options we chose are AWS’s user authentication policies, encrypting sensitive data fields, and using sufficient input validation to avoid injection attacks. Because of the lack of external tool support by NoSQL databases, we must resort to using modular security methods.\\

\noindent AWS’s user authentication policies, as well as encrypting sensitive data fields are extremely important to our database security. However, they can only be implemented by the AWS administrator; we, as developers, don’t have access. We can utilize sufficient input validation to avoid injection attacks. A benefit of implementing our NoSQL database with AWS DynamoDB is that it prevents common injection attacks by not allowing multiple operations with a single command. However, there do exist some lesser known vulnerabilities, and we will have to thoroughly research and test our solution.
	\subsection{Cost Comparison}
The final step after the completion of our project prototype is a comparison with a locally hosted solution, in order to see if our prototype will be adopted for use by OSU information services. They will be seeing if the cost to value ratio of our cloud prototype is greater than the value provided by local hardware. In order to fully represent the capabilities of our project, we will need to present a thorough, detailed model of the performance as the workload increases. As we get closer to the end, we will need to talk to our client in order to see what else we need for him to do a comprehensive comparison.