\section{Introduction}
	\subsection{Purpose}
    OSU campuses generate data constantly from multiples sources, including computer labs, wireless usage, student devices, and many others. This quantity of data, also known as big data, can effectively represent student behaviors for information technology. For example, analysis can be run to determine common student behaviors in order to allocate OSU resources to more often used utilities. Currently, the data is very difficult to manage because it is collected from multiple sources and is impossible to analyze. The data is neither stored in the same formats nor in the same locations, meaning it is inaccessible and useful information is unable to be extracted. The purpose of this project is to unify the data onto the consistent cloud platform of Amazon Web Services, which additionally provides utilities to manage and analyze.
    
    \subsection{Current Position}
    Currently, the functional part of the project is complete. We have a working database implementation in the Amazon Web Services public cloud, with appropriate storage, loading, and restricted access for sensitive data. By leveraging additional services in the AWS environment, we are able to provide rudimentary analysis, reporting, and visualization of data. From this position, we are able to present at Expo on the entire project, from beginning to end, including potential outcomes if the project were adopted by OSU. In the original project description, there were three deliverables listed. We have completed two of them: the database implementation and analysis/reporting/visualization. The third, a cost model, has yet to be complete. In order to provide an accurate cost model, we require an estimate for data amounts and are currently waiting for the estimate. This deliverable won't affect the project demonstration at Expo and is soley for the benefit of our client to decide on whether OSU will adopt our prototype.