\subsection{Isaac Chan}
\noindent I learned a bit more about different databases. I was previously aware of relational databases, specifically the more widely known AWS offering, Redshift. NoSQL with DynamoDB was new to me. However, I found that DynamoDB seemed to just a lazier version of Redshift because there was no upfront schema preparation, which might cause problems further on. Most of the other things, including workflow design, AWS utilities, I was already familiar with. \\

\noindent I think the most valuable non-technical information I learned was to constantly communicate with a client. I'm not sure if it was the balance of other classes or what, but during winter term, our communication with our client slipped a lot. We only met once or twice the entire term and he probably had no idea how we were progressing with his project. \\

\noindent In this project, it was very important to communicate with my group. We met a lot and were in constant communication, which helped us deliver on time and keep the schedule moving. I found it very helpful to develop a rough schedule and divide tasks early on. This meant that each of us was accountable for a portion and we progressed at a satisfactory rate. \\

\noindent If I could do it over again, I think I would have finished the project earlier on. The project itself was not very complex, but I felt like we were tied down by the structure of the class and how we were "supposed" to progress with it. Because of this, the project work was stretched out over winter and part of spring term, and it felt like we weren't doing a lot. \\