\subsection{Zhaoheng Wang}
    	 \noindent The technical information I learned is the process of big data analysis on Amazon Web Services. The project for my group is to deal with the big data on Amazon Web Services. It is brand-new project for me. It is difficult to figure out how to start this project without any background knowledge. Fortunately, the homepage of Amazon web Service gives the general steps about how to deal with the big data on Amazon Web Services. In general, the big data will be generated from multiple sources and the data file might be unreadable. Therefore, the first step is called parse data. The purpose of this step is to format the data file and make it readable. After that, the parsed data needs to store and organize the storage place such as database. After the data has been organized, the visualization graph for the data will be created for analyzing.This is the technical information I learned from the project. \\
         
         \noindent The non-technical information and project work I learned is how to figure out a brand-new question. I believe it is impossible to solve every problem in the future work just based on the current knowledge I have. Therefore, the steps for solving a brand-new question will be a very important skill to have. In this project, I started with discussing with client. After discussion, I summarized the purpose and requirements for this project. Then, I started to search keywords such as AWS, big data, analysis and many others for this topic. According to searching information, I narrowed down the requirements and designed the general workflow for the whole project. After that, I discussed the project with my teammates and client to ensure that I was going the right direction. Personally, I think this skill is one of the most important skill I learned from this project.\\
         
         \noindent As for the project management and team working, I have learned that good communication will make team work more efficient. Through good communication, I work with my group better. For example, one of my teammates has experience working on big data analysis. When I had some question about the project, I asked his advice. Another skill I learned from team is to manage time and make the schedule for the project. As for my group, our personal schedule conflicted with each other most of time. Because of this, we made the group schedule for the project and this schedule helped us to finish the requirements on time.\\
         
         \noindent If I could do it all over, I would like to research more information about the project such as workflow and tools because it is very helpful to have more background knowledge before starting a project. Without any background knowledge, I spent more time on searching than I would have liked. Take my project as an example, the project my group worked on is to deal with the big data on the Amazon web service. At first, I had no idea about how to start the project. Therefore, I searched online about the big data analysis. However, there are many ways to do that so it is hard to decide which is the best way for dealing with the big data. Besides, I was not familiar with Amazon web service. Thus, I could only guess the step before starting this project. Because of this, the process for asking the permission for using the tool was complicated.\\
         