\subsection{Zhi Jiang}
In the past three terms, I learned a lot of things from this project. From a technical point perspective, I learned and understood some basic workflow and framework of big data. I still learned some valuable tools of cloud computing. In our project, we mainly used Amazon Web Services. This cloud platform provides many useful services to complete all kinds of operation for big data. For example, S3 is used to store all original data as a data storage; DynamoDB is a kind of NoSQL database; EC2 is a virtual machine to connect other services and operate data on them. Moreover, according to this project, I learned the advantage of cloud computing on big data. For instance, cloud computing platform can avoid large capital expenditure on upgrades and hardware. On the other hand, it can also improve cost efficiency by more closely matching your cost pattern to your demand pattern. The purpose of the client setting up this project is he would like to compare the cost of cloud platform and local hardware. On the other hand, most cloud providers are extremely reliable in providing their services such as AWS. The security of data and project maintenance can be guaranteed significantly.\\ 

\noindent The most thing I did in project work is research. In our project, we must use several services on AWS. I have never used them before, so I started to do research for those services. I read developer guide and learned their basic operation method hence doing research is a very helpful point in project work. In fact, a programmer will always face problems he or she has never seen, so the research is the best approach to solving it. Moreover, I am glad that I had carefully considered the alternative solution. For some reasons, I had to give up the prior solution in our original plan and chose the alternative solution. Eventually, we still completed my portion by this alternative solution. In the whole developing process, the accident may occur at any time. A good alternative can help developer deal with emergencies and ensure that processes are running smoothly.\\

\noindent I still learned many things from project management. I believe that the schedule should be the most important component in the project management. As we know, there are many uncontrollable factors in the development process such as new requirements. If you have an unreasonable and chaotic schedule,  any uncontrollable factors will make the influence on your development. On the contrary, the perfect plan can let you know what you did, what you should do right now, and what you left. You can understand the status of your project.\\ 

\noindent Teamwork is a necessary basis for success. By getting along with my teammates in these three terms, I found many benefits from collaboration. First of all, teamwork can increase the development efficiency, but the precondition is every member of this team should do their duty. If someone is lazy on the team, it will affect the performance of the entire team. Secondly, teamwork can more efficiently produce the best idea. A team comes up a more effective solution than one person dealing with on the same problem because each member has different knowledge and perspective. Meanwhile, I still learned that it was important to respect ideas of everyone because members have different habits and work styles. When we have different opinions with each other, the most appropriate way is to calmly discuss rather than quarrel. Thirdly, I feel I can learn more knowledge in teamwork because everyone has some skills that you don’t know such as programming language or an editing tool.\\

\noindent If I could do it all over, I believe user interface should be a good choice for this project. After visualization of analysis, the user interface can show the results to students. On the other hand, students are probably able to enter their person information to know their data in the campus. 