\section{Methods of user interaction with the system}
        There will only be one type of user that interacts with the system - OSU staff that are able to manage and analyze the data. There are many analysis tools that can be used in conjunction with AWS. Most notably, Amazon Machine Learning (AML), Amazon EMR, and Amazon QuickSight. AML is a service that provides easy-to-use machine learning technology. Amazon EMR is a comprehensive utility that allows users to interact with databases, data warehouses, and customize their analysis. Amazon QuickSight is a fast business intelligence service that allows users to visualize data and provide responsive analysis. Our goal is to shape our implementation database to work with a utility that allows users to interact with our system. The ideal utility would provide tools to manage the data, provide analysis, machine learning support, and visualization.

        \begin{table}[ht]
        \centering
        \begin{tabular}{|c|c|c|c|c|}
            \hline
            \textbf{} & \textbf{Data Management} & \textbf{Analysis} & \textbf{Machine Learning} & \textbf{Visualization}\\
            \hline
            AML & No & No & Yes & No\\
            \hline
            EMR & Yes & Yes & Yes & No\\
            \hline
            QuickSight & No & Yes & No & Yes\\
            \hline
        \end{tabular}
        \end{table}

        \noindent AML is a very specific utility that only really offers machine learning analysis in a simple interface. It does contain much else within the tool, but the user can visualize the results from machine learning models with Amazon Cloudwatch.\\ 
        
        \noindent Amazon EMR is a comprehensive tool that can manage data and provide analysis, through conventional queries or machine learning technology. It is more difficult to use, and does not provide native visualization.\\ 

        \noindent Lastly, Amazon QuickSight is a business intelligence tool that can deliver fast analysis and boasts a very attractive visualization tool. However, more in-depth analysis and methods of data management are unavailable.\\

        \noindent Amazon EMR is the technology that we will primarily be considering. After the conclusion of our project, maintaining the database, as well as analysis, is critical to the survival of our prototype. Our chosen technology must support all of these, and Amazon EMR is the most comprehensive tool. However, in the end, all of these technologies can be used in conjunction with our final big data prototype, but it is important to have a primary tool in order to ensure database maintenance and analysis is continuable and extensible after the Expo.\\
    
%Zhi Jiang
%4