\begin{thebibliography}{1}
%Issac    
        \bibitem{I1}G. Kamat, "YCSB, the Open Standard for NoSQL Benchmarking, Joins Cloudera Labs", \textit{Cloudera}, 2015. Available: http://blog.cloudera.com/blog/2015/08/ycsb-the-open-standard-for-nosql-benchmarking-joins-cloudera-labs/. [Accessed: 14- Nov- 2016].
        
        \bibitem{I2}"TPC-H - Homepage", \textit{Tpc.org}, 2016. [Online]. Available: http://www.tpc.org/tpch/. [Accessed: 14- Nov- 2016].
%Zhi        
        \bibitem{Z1}M. Nemschoff, "Big data: 5 major advantages of Hadoop", \textit{IT Pro Portal}, 2013. [Online]. Available: http://www.itproportal.com/2013/12/20/big-data-5-major-advantages-of-hadoop/. [Accessed: 14- Nov- 2016].
        
        \bibitem{Z2}"What is Hadoop?", \textit{Amazon Web Services}, Inc., 2016. [Online]. Available: https://aws.amazon.com/emr/details/hadoop/?nc1{$=$}h\_ls. [Accessed: 14- Nov- 2016].
        
        \bibitem{Z3}S. Neumann, "Storing Apache Hadoop Data on the Cloud - HDFS vs. S3", \textit{Xplenty.com}, 2014. [Online]. Available: https://www.xplenty.com/blog/2014/03/storing-apache-hadoop-data-cloud-hdfs-vs-s3/. [Accessed: 14- Nov- 2016].
        
        \bibitem{Z4}L. Joseji, "6 Sparkling Features of Apache Spark!", \textit{dzone.com}, 2014. [Online]. Available: https://dzone.com/articles/6-sparkling-features-apache. [Accessed: 14- Nov- 2016].
        
        \bibitem{Z5}S. Neumann, "Spark vs. Hadoop MapReduce", \textit{Xplenty.com}, 2014. [Online]. Available: https://www.xplenty.com/blog/2014/11/apache-spark-vs-hadoop-mapreduce/. [Accessed: 14- Nov- 2016].
        
        \bibitem{Z6}"Amazon Kinesis Streams", \textit{Amazon Web Services, Inc.}, 2016. [Online]. Available: https://aws.amazon.com/kinesis/streams/?nc1{$=$}h\_ls. [Accessed: 14- Nov- 2016].
        
        \bibitem{Z7}"Apache Hive - Amazon EMR", \textit{Docs.aws.amazon.com}, 2016. [Online]. Available: http://docs.aws.amazon.com/ElasticMapReduce/latest/ReleaseGuide/emr-hive.html. [Accessed: 14- Nov- 2016].
        
        \bibitem{Z8}Amazon EMR - Developer guide. \textit{Amazon Web Services, Inc.}. [Online]. Available: http://docs.aws.amazon.com/ElasticMapReduce/latest/DeveloperGuide/emr-dg.pdf. [Accessed: 14- Nov- 2016].
        
%Zhaoheng        
        \bibitem{W1}"Why you probably shouldn't use cookies to store session data", \textit{Wonko.com}, 2008. [Online]. Available: http://wonko.com/post/why-you-probably-shouldnt-use-cookies-to-store-session-data. [Accessed: 14- Nov- 2016].
        
        \bibitem{W2}S. Knickelbine"Benefits of Using a Database", \textit{Work.chron.com}, 2016. [Online]. Available: http://work.chron.com/benefits-using-database-3792.html. [Accessed: 14- Nov- 2016].
        
        \bibitem{W3}"Advantages of Database", \textit{Ecomputernotes.com}, 2016. [Online]. Available: http://ecomputernotes.com/fundamental/what-is-a-database/advantages-of-database. [Accessed: 14- Nov- 2016].
        
        \bibitem{W4}D. Thakur"SQL vs NoSQL Database Differences Explained with few Example DB", \textit{Thegeekstuff.com}, 2016. [Online]. Available: http://www.thegeekstuff.com/2014/01/sql-vs-nosql-db/?utm\_source$=$tuicool. [Accessed: 14- Nov- 2016].
        
        \bibitem{W5}"Amazon DynamoDB Product Details", \textit{Amazon Web Services, Inc.}, 2016. [Online]. Available: https://aws.amazon.com/dynamodb/details/?nc1{$=$}h\_ls. [Accessed: 14- Nov- 2016].
        
        \bibitem{W6}"Amazon QuickSight Business Intelligence Software", \textit{Amazon Web Services, Inc.}, 2016. [Online]. Available: https://aws.amazon.com/quicksight/. [Accessed: 14- Nov- 2016].
    \end{thebibliography}