\section{The visualization tool use to display the data}
        There are various visualization tools could be using to make the data visualization. Each visualization tool has different features. Our goal for this part is to figure out the optimal choice of visualization tool for displaying the data. The visualization tool we choose to evaluate are Tableau,QuickSight and FusionChart. we generate several criteria for evaluating them such as platform, speed, features and cost.
        
        \begin{table}[ht]
        \centering
        \begin{tabular}{|c|c|c|p{8cm}|c|}
            \hline
            \textbf{Visualization Tool} & \textbf{Platform} & \textbf{Speed} & \textbf{Features} & \textbf{Cost}\\
            \hline
            Tableau & Tableau Online & Fast & Allows cross database, beautiful design & Low\\
            \hline
            QuickSight & Amazon Web Services & Fast & High accessibility, Get answer fast, Easy share business insight, Smart Visualizations & Low\\
            \hline
            FusionChart & No platform & Fast & Controllable for chart & Normal\\
            \hline
        \end{tabular}
        \end{table}
        
        \noindent Tableau could generate the graph fast and the cost of it is not high.  The QuickSight is supported by Amazon web services. It has high accessibility which allows access data from multiple source. Besides, it could share the business insight in security way.Another important feature for QuickSight is it could generate visualizations very fast for very large quantity of data.Furthermore, the cost of it is low\cite{W6}. FusionChart does not require the platform to support and it could generate the graph fast. The cost of Fusionchart is expensive than Tableau and QuickSight.\\


        \noindent Comparing with Tableau and FusionChart, the QuickSight is the optimal choice for our product. The QuickSight is supported by Amazon web services which fits the requirement of platform. Besides, it has strong accessibility which allows to communicate with other data service on Amazon web services such as Amazon DynamoDB easily.Furthermore, it has fast speed for generate the large data set which fits our purpose. Therefore, the QuickSight will be the optimal option as the visualization tool use to display the data.
        